### 2015-06-04 LOI/inc2.tex
minor changes

Manish Parashar, Rutgers, parashar@rutgers.edu, 732-445-5388
Carlson Malzahn, UCSC
Jay Lofstead, Sandia

@@

\begin{tabular}{| l| r| r| r| r| }
\hline
  \emph{Institution} & \emph{Year 1} & \emph{Year 2} & \emph{Year 3} \\
\hline
Oak Ridge National Laboratory & \$350,000 & \$350,000 & \$350,000	\\
\hline
  Argonne National Laboratory & \$350,000 & \$350,000 & \$350,000 \\
\hline
  Lawrence Berkeley Laboratory & \$300,000 & \$300,000 & \$300,000\\
\hline
  Brookhaven National Laboratory & \$150,000 & \$150,000 & \$150,000 \\
\hline
  Rutgers University & \$175,000 & \$175,000 & \$175,000 \\
\hline
  Stony Brook University & \$175,000 & \$175,000 & \$175,000 \\
\hline
  Total & \$1,500,000 & \$1,500,000 & \$1,500,000 \\
\hline
\end{tabular}
\newpage

@@

\underline{\textbf{Objectives:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into managing and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights xsinto
mission critical scientific processes in exascale compuxsting.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Cepth.
We will also take advantage of our staging system, Data Spaces, and our Comon communication Interface (CCI) and build on all of
our sucessful software used in petascale simulations to understand the new directions which need to be understood to fully develop
the next generation I/O and Storage System for exascale and beyond systems.

%
We will apply a technique which will re-organize and possibly reduce the total amount of information based on user intentions along
with direct feedback from the storage and I/O system to allow data to be optimized not just for output, but also for many of the complex
reading patterns. Since data analysis and visualization will be performed in both an in situ and post processing environment, 
we will continue to use our I/O and storage abstractions to help enable applications to take full advantage of the hardware and softare 
environments. Because data volumes are strictly outstripping available bandwidths, compression will
be required. Rather than focusing solely on lossless compression, we will
incorporate lossy compression with the ability to annotate data allowing
optimized algorithm selection based on the numerical methods employed in the
source simulation. We plan to epxlore this tradeoff of storage capacity and
bandwidth for computation to determine how to offer the user options that can
meet their needs with desireable performance characteristics.
%
Our objective is to reduce the time to knowledge, which means that we will also support additional access modes, beyond the traditional 
Checkpoint/Restart methods, and understand that all data has errors associated with it and we will ensure that these become encoded to allow
for additional optimizations. For example, all scientific simulations contain approximations, and all measurements from obervations and experiments 
also contain errors. These errors can help guide how information can be presented to users, by allowing us to ask for information within a given 
accuracy bound, and also allow us to offer a mode for recomputation vs. data storage and reterival.  
%
{\bf: please list other things from UCSC, OLCF}.
%

@@

The success of this project will  provide insights into how to build middleware and storage layers which can interact
well with each other, and take user-provided hints. Today data is reduced by application scientist who have 
limited information on what the storage layer can provide. They often make comprimises based on this limited knowledge
and either tune their output for writing or reading performance. This data then gets moved to other locations, and much of
the tuning is lost when the data is read back during their post processing. Furthermore, there is a limited set of operations
which users will be able to stage to other staging nodes for real-tiime-reduction and visualization.

>>>>

Manish Parashar, Rutgers, parashar@rutgers.edu, 732-445-5388
Carlson Malzahn, UCSC
Jay Lofstead, Sandia, gflofst@sandia.gov, 505-284-5803

@@

\begin{tabular}{| l| r| r| r| r| }
\hline
  \emph{Institution} & \emph{Year 1} & \emph{Year 2} & \emph{Year 3} \\
\hline
Oak Ridge National Laboratory & \$350,000 & \$350,000 & \$350,000	\\
\hline
  Rutgers University & \$175,000 & \$175,000 & \$175,000 \\
\hline
  University of California Santa Cruz & \$160,000 & \$160,000 & \$160,000 \\
\hline
  Sandia National Laboratories & \$360,000 & \$360,000 & \$360,000 \\
\hline
  Total & \$1,250,000 & \$1,250,000 & \$1,250,000 \\
\hline
\end{tabular}
\newpage

@@

\underline{\textbf{Objectives:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights into
mission critical scientific processes in exascale computing.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Ceph.
We will also take advantage of our staging system, Data Spaces, and our Comon communication Interface (CCI) and build on all of
our sucessful software used in petascale simulations to understand the new directions which need to be understood to fully develop
the next generation I/O and Storage System for exascale and beyond systems.

%
We will apply a technique which will re-organize and possibly reduce the total amount of information based on user intentions along
with direct feedback from the storage and I/O system to allow data to be optimized not just for output, but also for many of the complex
reading patterns. Since data analysis and visualization will be performed in both an in situ and post processing environment, 
we will continue to use our I/O and storage abstractions to help enable applications to take full advantage of the hardware and softare 
environments. Because data volumes are strictly outstripping available bandwidths, compression will
be required. Rather than focusing solely on lossless compression, we will
incorporate lossy compression with the ability to annotate data allowing
optimized algorithm selection based on the numerical methods employed in the
source simulation. We plan to explore this tradeoff of storage capacity and
bandwidth for computation to determine how to offer the user options that can
meet their needs with desireable performance characteristics.
%
Our objective is to reduce the time to knowledge, which means that we will also support additional access modes, beyond the traditional 
Checkpoint/Restart methods, and understand that all data has errors associated with it and we will ensure that these become encoded to allow
for additional optimizations. For example, all scientific simulations contain approximations, and all measurements from obervations and experiments 
also contain errors. These errors can help guide how information can be presented to users, by allowing us to ask for information within a given 
accuracy bound, and also allow us to offer a mode for recomputation vs. data storage and reterival.  
%
{\bf: please list other things from UCSC, OLCF}.
%

@@

The success of this project will  provide insights into how to build middleware and storage layers which can interact
well with each other, and take user-provided hints. Today data is reduced by application scientist who have 
limited information on what the storage layer can provide. They often make compromises based on this limited knowledge
and either tune their output for writing or reading performance. This data then gets moved to other locations, and much of
the tuning is lost when the data is read back during their post processing. Furthermore, there is a limited set of operations
which users will be able to stage to other staging nodes for real-tiime-reduction and visualization.
